### 2016-06-11 paper/icfp16-cameraready/evaluation.tex
start draft of user study section

>>>>

\input{gallery2}

\subsection{User Study}
\label{sec:user-study}
Finally, to test the explanatory power of our jump-compressed traces, we
ran a user study (IRB \#XXXX) at the University of Virginia (UVA).
%
We added four questions to an exam in the Spring session of UVA's
undergraduate Programming Languages course (CS XXX), in which presented
the students with ill-typed \ocaml\ programs and asked them to
%
(1) \emph{explain} the type error, and
%
(2) \emph{fix} the type error.
%
For each problem the student would be given the ill-typed program and
either \ocaml's error message or \toolname's jump-compressed trace.
%
The four problems assigned to the students were the
%
@sumList@, @digitsOfInt@, and @wwhile@ programs from \S~\ref{sec:advantage-traces}
as well as the following @append@ program....\ES{HERE}

We then instructed four annotators (one of whom is an author, the other
three were teaching assistants at UCSD) to classify the answers as
correct or incorrect.

We performed an inter-rater reliability (IRR) analysis to determine the
degree to which the annotators consistently graded the exams.
%
As we had more than two annotators assigning nominal ratings we used
Fleiss' kappa~\cite{XXX} to measure IRR.
%
The resulting kappa values, $\kappa = 0.72$ for the explanations and
$\kappa = 0.83$ for the fixes, indicate substantial agreement among
the annotators~\cite{XXX}.

The results of one of the annotators are shown in
Figure~\ref{fig:results-user-study}.
%
\begin{figure*}[t]
\centering
\includegraphics[width=0.49\linewidth]{user-study-reason.png}
\includegraphics[width=0.49\linewidth]{user-study-fix.png}
\caption{Results of the user study. The students given \toolname's
  jump-compressed trace consistently scored better than those
  given \ocaml's type error.}
\label{fig:results-user-study}
\end{figure*}
%
The students given \toolname's jump-compressed trace were consistently
more likely to correctly explain and fix the type error than those
given \ocaml's error message.
